\documentclass[11pt]{article}       % set main text size
\usepackage[a4paper,                % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font. comment this line out if you want to use the default LaTeX font Computer Modern
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-3pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=7pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Ianick Noejovich}

\vspace{6pt}

% contact information
\centerline{\href{mailto:iakanoe1056@gmail.com}{iakanoe1056@gmail.com} | \href{https://github.com/iakanoe}{github.com/iakanoe}}

\vspace{-6pt}

% experience section
\section*{Experience}

\textbf{Principal Mobile Developer,} \href{http://monks.com/}{Monks} -- Buenos Aires, Argentina \hfill 2022 -- Present \\
\vspace{-6pt}
\begin{itemize}
  \item Led development from zero to deployment of several "device demo" marketing apps for Google, some reaching over 5M monthly active users.
  \item Wrote a screenshot extraction tool to replace a standard two-month localization process that involved multiple teams, reducing the scope of each subsequent project by 16\% on average.
  \item Designed and managed all Google-related CI pipelines for mobile projects on Jenkins, including an interactive Slack bot that provided project managers with easy access to reports and artifacts.
  \item Developed a PoC for a custom RAG AI system based on AWS services.
  \item Built cross-project libraries and tools, both for development and other tasks including UI design, localized authoring and project management.
  \item Maintained multiple Android apps for business clients, including Starbucks, Progressive and Weber.
  \item Developed PoCs and conceptualized software products for client pitches.
  \item Earned a reputation as a problem-solving expert within the entire engineering team.
\end{itemize}

\vspace{3pt}

\textbf{Senior Android Engineer,} \href{https://fluxitsoft.com/}{Flux IT for Banco Galicia} -- Buenos Aires, Argentina \hfill 2021 -- 2022 \\
\vspace{-6pt}
\begin{itemize}
  \item Maintained and improved the personal and business banking apps for the largest private bank in the country, servicing over 2M monthly active users.
  \item Translated the core and UI modules for the business banking app from Java to Kotlin.
  \item Implemented a third party framework for biometric data validation.
  \item Restored development operations in one day after a legacy dependency repository was taken down by building an internal dependency caching system.
  \item Led the cross-squad initiative to translate all remaining source code from Java to Kotlin.
  \item Established standardized application of the MVVM pattern throughout the app by improving general documentation and giving training talks to fellow engineers.
\end{itemize}

\vspace{3pt}

\textbf{Technical Analyst,} \href{http://www.kinandcarta.com/}{Kin + Carta} -- Buenos Aires, Argentina \hfill 2020 -- 2021 \\
\vspace{-6pt}
\begin{itemize}
  \item Refactored and upgraded a legacy banking app for native Android and iOS. Repaired its CD pipeline to ensure robust deployment in the long term.
  \item Developed an internal web app for the HR team.
\end{itemize}

\vspace{3pt}

\textbf{Mobile Engineer,} \href{https://pisobredos.com/}{Pi Sobre Dos} -- Buenos Aires, Argentina \hfill 2019 -- 2020 \\
\vspace{-6pt}
\begin{itemize}
  \item Built a hybrid videcalling mobile app from zero to production using Ionic.
  \item Wrote a "blueprint" native Android app, which was later used internally to kickstart new projects.
\end{itemize}

\vspace{3pt}

\textbf{Full Stack Engineer,} {Freelance} -- Buenos Aires, Argentina \hfill 2015 -- 2021 \\
\vspace{-6pt}
\begin{itemize}
  \item Developed several web apps for small business clients using the MEAN stack.
\end{itemize}

% skills section
\section*{Skills}

\textbf{Frameworks/Tools:} Android (Jetpack Compose, MVVM, Dagger/Hilt, Room, Koin, Retrofit, NDK), CI/CD Tools (Jenkins, GitHub Actions, Travis CI), Docker, AWS Platform, Node.js, ARM Embedded, Ionic, Angular \\
\textbf{Languages:} Kotlin, Java, TypeScript, JavaScript, C, C++, Bash

% education section
\section*{Education}

\textbf{ORT Institute of Technology} -- Associate of Science in Systems Analysis \hfill Dec 2022 \\

\end{document}
